---
title: "Prototype implementation on DBpedia KB"
author: "Rifat"
date: "Monday, December 12, 2016"
output:
  pdf_document: default
  html_document: default
---

In this implementation we presents, Dbpedia 10 class quality analysis report based on four quality characteristics: (i) Persistency (ii) Historical Persistency (iii) Consistency (iv) Completeness. We divided the report based on each quality characteristics. Also we presented DBpedia growth analysis measure.

(i) [Class dbo Animal](#class-dbo-animal)
(ii) [Class dbo Artist](#class-dbo-artist)
(iii) [Class dbo Athlete](#class-dbo-athlete)
(iv) [Class dbo Film](#class-dbo-film)
(v) [Class dbo MusicalWork](#class-dbo-musicalwork)
(vi) [Class dbo Organisation](#class-dbo-organisation)
(vii) [Class dbo Place](#class-dbo-place)
(viii) [Class dbo Species](#class-dbo-species)
(ix) [Class dbo Work](#class-dbo-work)
(X) [Class foaf Person](#class-foaf-person)



##Quality Problem Report Overview

###Input

In this implementation the datasets is presented in folder "~/ExperimentalData/DBpedia" where each class property count over DBpedia 11 releases present in a CSV file. Also, the entity count of 10 classes presented in "DBpedia10ClassEntityCount.csv" file. 

```{r}
location="~/ExperimentalData/DBpedia/"
```

The dataset presented in the folder is already processed and build in a intermediate data structure for the quality assessment approach.

To run the rmd file only need to specify the folder location for input data.


###Results Structure

(i) Persistency: A line graph presented to visualize variation on last two DBpedia Release.

(i) Historical Persistency: A table with this classes with persistency issues over the 11 Releases.

(iii) Consistency: Result of property values presented in a table. 1st table with incorrect property values and 2nd table with filtered property values

(iv) Completeness: Result of property values presented in a table with normalized property values and difference between two version of normalized property values.

(v) KB growth: A graph visualizing KB growth.


## Experiment Results

Input: Set Entity file location such as -

```{r}
location<- "/ExperimentalData/DBpedia/"
```

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}

# List of library

library(ggplot2)
library(plyr)
library(dplyr)
library(dtplyr)
library(reshape2)
library(hts)
library('knitr')
library(reshape2)
#Implementation of consistency and completeness measures
#Input entity files

loc<-paste(getwd(),location,sep = "")

loc<-paste(loc,"DBpedia10ClassEntityCount.csv",sep = "")

#location<- "C:/Users/rifat/Desktop/R_milan/githubRepo/KBQ2/ExperimentalData/DBpedia/DBpedia10ClassEntityCount.csv"
entityDataSet <- read.csv(loc)
unclass=unique(entityDataSet$class)

source("helper.R")



entityWithDays= ddply(entityDataSet,.(class), here(transform), days=fn(Release))

```


### Class dbo Animal

[http://dbpedia.org/ontology/Animal]

Input: set file location such as -

```{r}
location<- "/ExperimentalData/DBpedia/"
```


```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}

#location<- "C:/Users/rifat/Desktop/R_milan/githubRepo/KBQ2/ExperimentalData/DBpedia/dbo-Animal.csv"

loc<-paste(getwd(),location,sep = "")

loc<-paste(loc,"dbo-Animal.csv",sep = "")
dTproperty <- read.csv(loc,header = TRUE)

dTproperty=plyr::rename(dTproperty, c("count33"="2009-05-20", "count34"="2009-09-20","count201504"="2015-02-05","count201510"="2015-10-02","count35"="2010-03-16","count36"="2010-10-11",
                           "count37"="2011-07-22","count38"="2012-06-01","count39"="2013-0-03","count40"="2014-05-02","count35.1"="2016-04-01"))

entityData=entityDataSet[entityDataSet$class==unclass[1],]

p<-persistencyPlot(entityData)

```


#### Persistency

Persistency Measure Result:  `r entityData[nrow(entityData),3]` value  `r entityData[nrow(entityData),4]` < `r entityData[nrow(entityData)-1,3]` value  `r entityData[nrow(entityData)-1,4]`. So Persistency=  `r persistencyMeasure(entityData)`
Entity Count for 11 Release:

```{r,echo=FALSE}
kable(entityData[,-c(1)], format = "markdown")
shadeAreaP(p,entityData)

```


#### Historical Persitency

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}
histPer<-histPerAll(entityData)

```

Historical Persistency Measure Result: Total no. of class = `r length(unclass)` and No. of persistency=`r nrow(histPer[histPer$Persistency==0,])`. HistPersistencyMeasure= `r HistPersistencyMeasure(histPer)` %

Releases with persistency values:

```{r,echo=FALSE}
kable(histPer[,-c(1)], format = "markdown")
```




#### Consistency

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}

FilteredProperty<-FilteredPropertyfun(dTproperty,entityDataSet)
TwoSeriesData<-TwoSeriesDataFun(dTproperty,entityDataSet)
dataSet<-dataSetFun(dTproperty,entityDataSet)
consistencyData<-consistencyDataFun(dTproperty,entityDataSet)

```

No. of inconsistent property = `r nrow(FilteredProperty)`


```{r,echo=FALSE}
#kable(SubSetProp, format = "markdown")

kable(FilteredProperty, format = "markdown")

#head(FilteredProperty)

```

List of Consistent Property over last two version:

```{r,echo=FALSE}
kable(TwoSeriesData, format = "markdown")

n=nrow(TwoSeriesData)+nrow(FilteredProperty)


```

#### Completeness

Total no. of property =`r n` No. of Consistent Property = `r nrow(TwoSeriesData)` No. of incomplete property = `r nrow(consistencyData)`

Percentage of completeness= `r ((nrow(TwoSeriesData)-nrow(consistencyData))/nrow(TwoSeriesData)) *100` %


List of inincomplete property:

```{r,echo=FALSE}
kable(dataSet, format = "markdown")

```

#### KB growth 


```{r,echo=FALSE}

entity<-entityWithDays[entityWithDays$class==unclass[1],]

ND<-NormDist(entity)

graph<-plotEntity(entity)

graph

stab<-CheckND(ND)

```
The normalized distance(ND)= `r ND`

KB growth condition is 1 if ND<1 or KB growth is 0 if ND>=1

KB growth=`r stab`

### Class dbo Artist

[http://dbpedia.org/ontology/Artist]

Input: Set file location such as -

```{r}
location<- "/ExperimentalData/DBpedia/"
```

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}

#location<- "C:/Users/rifat/Desktop/R_milan/githubRepo/KBQ2/ExperimentalData/DBpedia/dbo-Artist.csv"
#dTproperty <- read.csv(location,header = TRUE)

loc<-paste(getwd(),location,sep = "")

loc<-paste(loc,"dbo-Artist.csv",sep = "")
dTproperty <- read.csv(loc,header = TRUE)


dTproperty=plyr::rename(dTproperty, c("count33"="2009-05-20", "count34"="2009-09-20","count201504"="2015-02-05","count201510"="2015-10-02","count35"="2010-03-16","count36"="2010-10-11",
                           "count37"="2011-07-22","count38"="2012-06-01","count39"="2013-0-03","count40"="2014-05-02","count35.1"="2016-04-01"))


entityData=entityDataSet[entityDataSet$class==unclass[2],]

p<-persistencyPlot(entityData)

```

#### Persistency

Persistency Measure Result:  `r entityData[nrow(entityData),3]` value  `r entityData[nrow(entityData),4]` < `r entityData[nrow(entityData)-1,3]` value  `r entityData[nrow(entityData)-1,4]`. So Persistency=  `r persistencyMeasure(entityData)`
Entity Count for 11 Release:

```{r,echo=FALSE}
kable(entityData[,-c(1)], format = "markdown")
shadeAreaP(p,entityData)

```


#### Historical Persitency

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}
histPer<-histPerAll(entityData)

```

Historical Persistency Measure Result: Total no. of class = `r length(unclass)` and No. of persistency=`r nrow(histPer[histPer$Persistency==0,])`. HistPersistencyMeasure= `r HistPersistencyMeasure(histPer)` %

Releases with persistency values:

```{r,echo=FALSE}
kable(histPer[,-c(1)], format = "markdown")
```


#### Consistency


```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}


FilteredProperty<-FilteredPropertyfun(dTproperty,entityDataSet)
TwoSeriesData<-TwoSeriesDataFun(dTproperty,entityDataSet)
dataSet<-dataSetFun(dTproperty,entityDataSet)
consistencyData<-consistencyDataFun(dTproperty,entityDataSet)

```

No. of inconsistent property = `r nrow(FilteredProperty)`


```{r,echo=FALSE}
#kable(SubSetProp, format = "markdown")

kable(FilteredProperty, format = "markdown")

#head(FilteredProperty)

```

List of Consistent Property over last two version:

```{r,echo=FALSE}
kable(TwoSeriesData, format = "markdown")

n=nrow(TwoSeriesData)+nrow(FilteredProperty)


```

#### Completeness


Total no. of property =`r n` No. of Consistent Property = `r nrow(TwoSeriesData)` No. of incomplete property = `r nrow(consistencyData)`

Percentage of completeness= `r ((nrow(TwoSeriesData)-nrow(consistencyData))/nrow(TwoSeriesData)) *100` %

List of inincomplete property:

```{r,echo=FALSE}
kable(dataSet, format = "markdown")

```

#### KB growth 


```{r,echo=FALSE}

entity<-entityWithDays[entityWithDays$class==unclass[2],]

ND<-NormDist(entity)

graph<-plotEntity(entity)

graph

stab<-CheckND(ND)

```
The normalized distance(ND)= `r ND`

KB growth condition is 1 if ND<1 or KB growth is 0 if ND>=1

KB growth=`r stab`

### Class dbo Athlete

[http://dbpedia.org/ontology/Athlete]

Input: Set file location such as -

```{r}
location<- "/ExperimentalData/DBpedia/"
```

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}

#location<- "C:/Users/rifat/Desktop/R_milan/githubRepo/KBQ2/ExperimentalData/DBpedia/dbo-athlete.csv"
#dTproperty <- read.csv(location,header = TRUE)

loc<-paste(getwd(),location,sep = "")

loc<-paste(loc,"dbo-athlete.csv",sep = "")
dTproperty <- read.csv(loc,header = TRUE)


dTproperty=plyr::rename(dTproperty, c("count33"="2009-05-20", "count34"="2009-09-20","count201504"="2015-02-05","count201510"="2015-10-02","count35"="2010-03-16","count36"="2010-10-11",
                           "count37"="2011-07-22","count38"="2012-06-01","count39"="2013-0-03","count40"="2014-05-02","count35.1"="2016-04-01"))


entityData=entityDataSet[entityDataSet$class==unclass[3],]

p<-persistencyPlot(entityData)

```

#### Persistency

Persistency Measure Result:  `r entityData[nrow(entityData),3]` value  `r entityData[nrow(entityData),4]` < `r entityData[nrow(entityData)-1,3]` value  `r entityData[nrow(entityData)-1,4]`. So Persistency=  `r persistencyMeasure(entityData)`
Entity Count for 11 Release:

```{r,echo=FALSE}
kable(entityData[,-c(1)], format = "markdown")
shadeAreaP(p,entityData)

```


#### Historical Persitency

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}
histPer<-histPerAll(entityData)

```

Historical Persistency Measure Result: Total no. of class = `r length(unclass)` and No. of persistency=`r nrow(histPer[histPer$Persistency==0,])`. HistPersistencyMeasure= `r HistPersistencyMeasure(histPer)` %

Releases with persistency values:

```{r,echo=FALSE}
kable(histPer[,-c(1)], format = "markdown")
```

#### Consistency


```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}


unclass=unique(entityWithDays$class)

en=entityDataSet[entityDataSet$class==unclass[3],]

# dTproperty=normalize(dTproperty,en)

dTproperty<-dTproperty[,order(colnames(dTproperty),decreasing=TRUE)]

#write.csv(dTproperty, file = "C:/Users/rifat/Desktop/R_milan/githubRepo/KBQ2/ExperimentalData/DBpedia/dbo-athlete.csv")

NondTproperty=dTproperty

NondTproperty=dTproperty

CorrectProperty = identifyCorrectProperty(dTproperty,en)

# InCorrectPropery= identifyInCorrectProperty(NondTproperty,en)


avg=(en[11,]$count+en[10,]$count+en[9,]$count)/3

NondTproperty=dTproperty

d=3
t=11

for(i in 1:11){
     
  countEntity=100#avg/20000#en[t,]$count/10000
  
#   print(countEntity)  
#   print(length(dTproperty[,d]))

  Nonprop=NondTproperty[,d]
  
  for(j in 1:length(Nonprop)){
      
       if(Nonprop[j]>countEntity){
         Nonprop[j]=0
       }
       else{
         Nonprop[j]=Nonprop[j]        
       }
  }
  print(Nonprop)  
  NondTproperty[,d]=Nonprop
  d=d+1
  t=t-1
}

require(data.table)
DT=data.table(NondTproperty)

listCol <- colnames(DT)[grep("-", colnames(DT))]

DT[, Sum := Reduce('+', .SD), .SDcols=listCol][]

NonRproperty=data.frame(DT)

IncorrectProperty=NonRproperty[NonRproperty$Sum!=0,]

head(IncorrectProperty)

# return(IncorrectProperty)


# nrow(NonRproperty)-nrow(IncorrectProperty)
# 
# nrow(Rproperty)-nrow(CorrectProperty)

NdTproperty=CorrectProperty[,-c(14)]

propertySubSet=data.frame(property=IncorrectProperty[,1],v201604=IncorrectProperty[,3],v201510=IncorrectProperty[,4],v201502=IncorrectProperty[,5])


require(data.table)
DT=data.table(propertySubSet)

listCol <- colnames(DT)[grep("v", colnames(DT))]

DT[, Sum := Reduce('+', .SD), .SDcols=listCol][]

propertySubSet=data.frame(DT)

FilteredProperty=propertySubSet[propertySubSet$Sum!=0,]

FilteredProperty=FilteredProperty[,-c(5)]

nrow(FilteredProperty)

CorrectProperty = identifyCorrectProperty(dTproperty,en)

InCorrectPropery= identifyInCorrectProperty(NondTproperty,en)

SubSetProp=SubSetProperty(NondTproperty,en)

# nrow(NonRproperty)-nrow(IncorrectProperty)
# 
# nrow(Rproperty)-nrow(CorrectProperty)

NdTproperty=CorrectProperty[,-c(14)]

# normalize(NdTproperty,en)
d=3
t=11
for(i in 1:11){

    norm= NdTproperty[,d]/en[t,]$count

    NdTproperty[,d]=norm
    d=d+1
#     print(norm)
    t=t-1
}

NdTproperty$diffLast=NdTproperty[,3]-NdTproperty[,4]

# print(dTproperty)
# head(dTproperty)

# NdTproperty$diffLast=dTproperty[,3]-dTproperty[,4]

consistencyData=NdTproperty[NdTproperty$diffLast<0,]

nrow(dTproperty)

nrow(consistencyData)

dataSet=data.frame(property=consistencyData$property,Version201604=consistencyData$X2016.04.01,Version201510=consistencyData$X2015.10.02,NormFreqDiff=consistencyData$diffLast)

entityVal=en

entityVal$WeightValue=en$count/10000

CorrectProperty$diff=CorrectProperty[,3]+CorrectProperty[,4]

TwoSeries=CorrectProperty[CorrectProperty$diff!=0,]

TwoSeriesData=data.frame(property=TwoSeries$property,v201604=TwoSeries$X2016.04.01,v201510=TwoSeries$X2015.10.02,v201504=TwoSeries$X2015.02.05)


InCdata=data.frame(Property=InCorrectPropery$property,v201604=InCorrectPropery$X2016.04.01,v201510=InCorrectPropery$X2015.10.02,v201502=InCorrectPropery$X2015.02.05)


```

No. of inconsistent property = `r nrow(FilteredProperty)`


```{r,echo=FALSE}
#kable(SubSetProp, format = "markdown")

kable(FilteredProperty, format = "markdown")

#head(FilteredProperty)

```

List of Consistent Property over last two version:

```{r,echo=FALSE}
kable(TwoSeriesData, format = "markdown")

n=nrow(TwoSeriesData)+nrow(FilteredProperty)


```

#### Completeness


Total no. of property =`r n` No. of Consistent Property = `r nrow(TwoSeriesData)` No. of incomplete property = `r nrow(consistencyData)`

Percentage of completeness= `r ((nrow(TwoSeriesData)-nrow(consistencyData))/nrow(TwoSeriesData)) *100` %

List of inincomplete property:

```{r,echo=FALSE}
kable(dataSet, format = "markdown")

```

#### KB growth 


```{r,echo=FALSE}

entity<-entityWithDays[entityWithDays$class==unclass[3],]

ND<-NormDist(entity)

graph<-plotEntity(entity)

graph

stab<-CheckND(ND)

```
The normalized distance(ND)= `r ND`

KB growth condition is 1 if ND<1 or KB growth is 0 if ND>=1

KB growth=`r stab`


### Class dbo Film

[http://dbpedia.org/ontology/Film]

Input: Set file location such as -

```{r}
location<- "/ExperimentalData/DBpedia/"
```

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}

# location<- "C:/Users/rifat/Desktop/R_milan/githubRepo/KBQ2/ExperimentalData/DBpedia/dbo-film.csv"
# dTproperty <- read.csv(location,header = TRUE)

loc<-paste(getwd(),location,sep = "")

loc<-paste(loc,"dbo-film.csv",sep = "")
dTproperty <- read.csv(loc,header = TRUE)


dTproperty=plyr::rename(dTproperty, c("count33"="2009-05-20", "count34"="2009-09-20","count201504"="2015-02-05","count201510"="2015-10-02","count35"="2010-03-16","count36"="2010-10-11",
                           "count37"="2011-07-22","count38"="2012-06-01","count39"="2013-0-03","count40"="2014-05-02","count35.1"="2016-04-01"))


entityData=entityDataSet[entityDataSet$class==unclass[4],]

p<-persistencyPlot(entityData)

```

#### Persistency

Persistency Measure Result:  `r entityData[nrow(entityData),3]` value  `r entityData[nrow(entityData),4]` < `r entityData[nrow(entityData)-1,3]` value  `r entityData[nrow(entityData)-1,4]`. So Persistency=  `r persistencyMeasure(entityData)`
Entity Count for 11 Release:

```{r,echo=FALSE}
kable(entityData[,-c(1)], format = "markdown")
shadeAreaP(p,entityData)

```


#### Historical Persitency

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}
histPer<-histPerAll(entityData)

```

Historical Persistency Measure Result: Total no. of class = `r length(unclass)` and No. of persistency=`r nrow(histPer[histPer$Persistency==0,])`. HistPersistencyMeasure= `r HistPersistencyMeasure(histPer)` %

Releases with persistency values:

```{r,echo=FALSE}
kable(histPer[,-c(1)], format = "markdown")
```




#### Consistency


```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}


FilteredProperty<-FilteredPropertyfun(dTproperty,entityDataSet)
TwoSeriesData<-TwoSeriesDataFun(dTproperty,entityDataSet)
dataSet<-dataSetFun(dTproperty,entityDataSet)
consistencyData<-consistencyDataFun(dTproperty,entityDataSet)

```

No. of inconsistent property = `r nrow(FilteredProperty)`


```{r,echo=FALSE}
#kable(SubSetProp, format = "markdown")

kable(FilteredProperty, format = "markdown")

#head(FilteredProperty)

```

List of Consistent Property over last two version:

```{r,echo=FALSE}
kable(TwoSeriesData, format = "markdown")

n=nrow(TwoSeriesData)+nrow(FilteredProperty)


```

#### Completeness

Total no. of property =`r n` No. of Consistent Property = `r nrow(TwoSeriesData)` No. of incomplete property = `r nrow(consistencyData)`

Percentage of completeness= `r ((nrow(TwoSeriesData)-nrow(consistencyData))/nrow(TwoSeriesData)) *100` %

List of inincomplete property:

```{r,echo=FALSE}
kable(dataSet, format = "markdown")

```

#### KB growth 


```{r,echo=FALSE}

entity<-entityWithDays[entityWithDays$class==unclass[4],]

ND<-NormDist(entity)

graph<-plotEntity(entity)

graph

stab<-CheckND(ND)

```
The normalized distance(ND)= `r ND`

KB growth condition is 1 if ND<1 or KB growth is 0 if ND>=1

KB growth=`r stab`

### Class dbo MusicalWork

[http://dbpedia.org/ontology/MusicalWork]

Input: Set file location such as -

```{r}
location<- "/ExperimentalData/DBpedia/"
```

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}

# location<- "C:/Users/rifat/Desktop/R_milan/githubRepo/KBQ2/ExperimentalData/DBpedia/dbo-musicalWork.csv"
# dTproperty <- read.csv(location,header = TRUE)

loc<-paste(getwd(),location,sep = "")

loc<-paste(loc,"dbo-musicalWork.csv",sep = "")
dTproperty <- read.csv(loc,header = TRUE)


dTproperty=plyr::rename(dTproperty, c("count33"="2009-05-20", "count34"="2009-09-20","count201504"="2015-02-05","count201510"="2015-10-02","count35"="2010-03-16","count36"="2010-10-11",
                           "count37"="2011-07-22","count38"="2012-06-01","count39"="2013-0-03","count40"="2014-05-02","count35.1"="2016-04-01"))


entityData=entityDataSet[entityDataSet$class==unclass[5],]

p<-persistencyPlot(entityData)

```

#### Persistency

Persistency Measure Result:  `r entityData[nrow(entityData),3]` value  `r entityData[nrow(entityData),4]` < `r entityData[nrow(entityData)-1,3]` value  `r entityData[nrow(entityData)-1,4]`. So Persistency=  `r persistencyMeasure(entityData)`
Entity Count for 11 Release:

```{r,echo=FALSE}
kable(entityData[,-c(1)], format = "markdown")
shadeAreaP(p,entityData)

```


#### Historical Persitency

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}
histPer<-histPerAll(entityData)

```

Historical Persistency Measure Result: Total no. of class = `r length(unclass)` and No. of persistency=`r nrow(histPer[histPer$Persistency==0,])`. HistPersistencyMeasure= `r HistPersistencyMeasure(histPer)` %

Releases with persistency values:

```{r,echo=FALSE}
kable(histPer[,-c(1)], format = "markdown")
```


#### Consistency


```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}


FilteredProperty<-FilteredPropertyfun(dTproperty,entityDataSet)
TwoSeriesData<-TwoSeriesDataFun(dTproperty,entityDataSet)
dataSet<-dataSetFun(dTproperty,entityDataSet)
consistencyData<-consistencyDataFun(dTproperty,entityDataSet)

```

No. of inconsistent property = `r nrow(FilteredProperty)`


```{r,echo=FALSE}
#kable(SubSetProp, format = "markdown")

kable(FilteredProperty, format = "markdown")

#head(FilteredProperty)

```

List of Consistent Property over last two Releases:

```{r,echo=FALSE}
kable(TwoSeriesData, format = "markdown")

n=nrow(TwoSeriesData)+nrow(FilteredProperty)


```

#### Completeness

Total no. of property =`r n` No. of Consistent Property = `r nrow(TwoSeriesData)` No. of incomplete property = `r nrow(consistencyData)`

Percentage of completeness= `r ((nrow(TwoSeriesData)-nrow(consistencyData))/nrow(TwoSeriesData)) *100` %

List of inincomplete property:

```{r,echo=FALSE}
kable(dataSet, format = "markdown")

```

#### KB growth 


```{r,echo=FALSE}

entity<-entityWithDays[entityWithDays$class==unclass[5],]

ND<-NormDist(entity)

graph<-plotEntity(entity)

graph

stab<-CheckND(ND)

```
The normalized distance(ND)= `r ND`

KB growth condition is 1 if ND<1 or KB growth is 0 if ND>=1

KB growth=`r stab`

### Class dbo Organisation

[http://dbpedia.org/ontology/Organisation]

Input: Set file location such as -

```{r}
location<- "/ExperimentalData/DBpedia/"
```

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}

# location<- "C:/Users/rifat/Desktop/R_milan/githubRepo/KBQ2/ExperimentalData/DBpedia/dbo-organisation.csv"
# dTproperty <- read.csv(location,header = TRUE)

loc<-paste(getwd(),location,sep = "")

loc<-paste(loc,"dbo-organisation.csv",sep = "")
dTproperty <- read.csv(loc,header = TRUE)


dTproperty=plyr::rename(dTproperty, c("count33"="2009-05-20", "count34"="2009-09-20","count201504"="2015-02-05","count201510"="2015-10-02","count35"="2010-03-16","count36"="2010-10-11",
                           "count37"="2011-07-22","count38"="2012-06-01","count39"="2013-0-03","count40"="2014-05-02","count35.1"="2016-04-01"))


entityData=entityDataSet[entityDataSet$class==unclass[6],]

p<-persistencyPlot(entityData)

```

#### Persistency

Persistency Measure Result:  `r entityData[nrow(entityData),3]` value  `r entityData[nrow(entityData),4]` < `r entityData[nrow(entityData)-1,3]` value  `r entityData[nrow(entityData)-1,4]`. So Persistency=  `r persistencyMeasure(entityData)`
Entity Count for 11 Release:

```{r,echo=FALSE}
kable(entityData[,-c(1)], format = "markdown")
shadeAreaP(p,entityData)

```


#### Historical Persitency

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}
histPer<-histPerAll(entityData)

```

Historical Persistency Measure Result: Total no. of class = `r length(unclass)` and No. of persistency=`r nrow(histPer[histPer$Persistency==0,])`. HistPersistencyMeasure= `r HistPersistencyMeasure(histPer)` %

Releases with persistency values:

```{r,echo=FALSE}
kable(histPer[,-c(1)], format = "markdown")
```

#### Consistency


```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}


FilteredProperty<-FilteredPropertyfun(dTproperty,entityDataSet)
TwoSeriesData<-TwoSeriesDataFun(dTproperty,entityDataSet)
dataSet<-dataSetFun(dTproperty,entityDataSet)
consistencyData<-consistencyDataFun(dTproperty,entityDataSet)

```

No. of inconsistent property = `r nrow(FilteredProperty)`


```{r,echo=FALSE}
#kable(SubSetProp, format = "markdown")

kable(FilteredProperty, format = "markdown")

#head(FilteredProperty)

```

List of Consistent Property over last two version:

```{r,echo=FALSE}
kable(TwoSeriesData, format = "markdown")

n=nrow(TwoSeriesData)+nrow(FilteredProperty)


```

#### Completeness


Total no. of property =`r n` No. of Consistent Property = `r nrow(TwoSeriesData)` No. of incomplete property = `r nrow(consistencyData)`

Percentage of completeness= `r ((nrow(TwoSeriesData)-nrow(consistencyData))/nrow(TwoSeriesData)) *100` %

List of inincomplete property:

```{r,echo=FALSE}
kable(dataSet, format = "markdown")

```

#### KB growth 


```{r,echo=FALSE}

entity<-entityWithDays[entityWithDays$class==unclass[6],]

ND<-NormDist(entity)

graph<-plotEntity(entity)

graph

stab<-CheckND(ND)

```
The normalized distance(ND)= `r ND`

KB growth is 1 if ND<1 or KB growth is 0 if ND>=1

KB growth=`r stab`


### Class dbo Place

[http://dbpedia.org/ontology/Place]

Input: Set file location such as -

```{r}
location<- "/ExperimentalData/DBpedia/"
```

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}

# location<- "C:/Users/rifat/Desktop/R_milan/githubRepo/KBQ2/ExperimentalData/DBpedia/dbo-place.csv"
# dTproperty <- read.csv(location,header = TRUE)

loc<-paste(getwd(),location,sep = "")
loc<-paste(loc,"dbo-place.csv",sep = "")
dTproperty <- read.csv(loc,header = TRUE)

dTproperty=plyr::rename(dTproperty, c("count33"="2009-05-20", "count34"="2009-09-20","count201504"="2015-02-05","count201510"="2015-10-02","count35"="2010-03-16","count36"="2010-10-11",
                           "count37"="2011-07-22","count38"="2012-06-01","count39"="2013-0-03","count40"="2014-05-02","count35.1"="2016-04-01"))


entityData=entityDataSet[entityDataSet$class==unclass[7],]

p<-persistencyPlot(entityData)

```

#### Persistency

Persistency Measure Result:  `r entityData[nrow(entityData),3]` value  `r entityData[nrow(entityData),4]` < `r entityData[nrow(entityData)-1,3]` value  `r entityData[nrow(entityData)-1,4]`. So Persistency=  `r persistencyMeasure(entityData)`
Entity Count for 11 Release:

```{r,echo=FALSE}
kable(entityData[,-c(1)], format = "markdown")
shadeAreaP(p,entityData)

```


#### Historical Persitency

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}
histPer<-histPerAll(entityData)

```

Historical Persistency Measure Result: Total no. of class = `r length(unclass)` and No. of persistency=`r nrow(histPer[histPer$Persistency==0,])`. HistPersistencyMeasure= `r HistPersistencyMeasure(histPer)` %

Releases with persistency values:

```{r,echo=FALSE}
kable(histPer[,-c(1)], format = "markdown")
```

#### Consistency


```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}


FilteredProperty<-FilteredPropertyfun(dTproperty,entityDataSet)
TwoSeriesData<-TwoSeriesDataFun(dTproperty,entityDataSet)
dataSet<-dataSetFun(dTproperty,entityDataSet)
consistencyData<-consistencyDataFun(dTproperty,entityDataSet)

```

No. of inconsistent property = `r nrow(FilteredProperty)`


```{r,echo=FALSE}
#kable(SubSetProp, format = "markdown")

kable(FilteredProperty, format = "markdown")

#head(FilteredProperty)

```

List of Consistent Property over last two version:

```{r,echo=FALSE}
kable(TwoSeriesData, format = "markdown")

n=nrow(TwoSeriesData)+nrow(FilteredProperty)


```

#### Completeness

Total no. of property =`r n` No. of Consistent Property = `r nrow(TwoSeriesData)` No. of incomplete property = `r nrow(consistencyData)`

Percentage of completeness= `r ((nrow(TwoSeriesData)-nrow(consistencyData))/nrow(TwoSeriesData)) *100` %

List of inincomplete property:

```{r,echo=FALSE}
kable(dataSet, format = "markdown")

```

#### KB growth 


```{r,echo=FALSE}

entity<-entityWithDays[entityWithDays$class==unclass[7],]

ND<-NormDist(entity)

graph<-plotEntity(entity)

graph

stab<-CheckND(ND)

```
The normalized distance(ND)= `r ND`

KB growth condition is 1 if ND<1 or KB growth is 0 if ND>=1

KB growth=`r stab`

### Class dbo Species

[http://dbpedia.org/ontology/Species]

Input: Set file location such as -

```{r}
location<- "/ExperimentalData/DBpedia/"
```

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}
# 
# location<- "C:/Users/rifat/Desktop/R_milan/githubRepo/KBQ2/ExperimentalData/DBpedia/dbo-species.csv"
# dTproperty <- read.csv(location,header = TRUE)

loc<-paste(getwd(),location,sep = "")

loc<-paste(loc,"dbo-species.csv",sep = "")
dTproperty <- read.csv(loc,header = TRUE)

dTproperty=plyr::rename(dTproperty, c("count33"="2009-05-20", "count34"="2009-09-20","count201504"="2015-02-05","count201510"="2015-10-02","count35"="2010-03-16","count36"="2010-10-11",
                           "count37"="2011-07-22","count38"="2012-06-01","count39"="2013-0-03","count40"="2014-05-02","count35.1"="2016-04-01"))


entityData=entityDataSet[entityDataSet$class==unclass[8],]

p<-persistencyPlot(entityData)

```

#### Persistency

Persistency Measure Result:  `r entityData[nrow(entityData),3]` value  `r entityData[nrow(entityData),4]` < `r entityData[nrow(entityData)-1,3]` value  `r entityData[nrow(entityData)-1,4]`. So Persistency=  `r persistencyMeasure(entityData)`
Entity Count for 11 Release:

```{r,echo=FALSE}
kable(entityData[,-c(1)], format = "markdown")
shadeAreaP(p,entityData)

```


#### Historical Persitency

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}
histPer<-histPerAll(entityData)

```

Historical Persistency Measure Result: Total no. of class = `r length(unclass)` and No. of persistency=`r nrow(histPer[histPer$Persistency==0,])`. HistPersistencyMeasure= `r HistPersistencyMeasure(histPer)` %

Releases with persistency values:

```{r,echo=FALSE}
kable(histPer[,-c(1)], format = "markdown")
```


#### Consistency


```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}


FilteredProperty<-FilteredPropertyfun(dTproperty,entityDataSet)
TwoSeriesData<-TwoSeriesDataFun(dTproperty,entityDataSet)
dataSet<-dataSetFun(dTproperty,entityDataSet)
consistencyData<-consistencyDataFun(dTproperty,entityDataSet)

```

No. of inconsistent property = `r nrow(FilteredProperty)`


```{r,echo=FALSE}
#kable(SubSetProp, format = "markdown")

kable(FilteredProperty, format = "markdown")

#head(FilteredProperty)

```

List of Consistent Property over last two version:

```{r,echo=FALSE}
kable(TwoSeriesData, format = "markdown")

n=nrow(TwoSeriesData)+nrow(FilteredProperty)


```

#### Completeness


Total no. of property =`r n` No. of Consistent Property = `r nrow(TwoSeriesData)` No. of incomplete property = `r nrow(consistencyData)`

Percentage of completeness= `r ((nrow(TwoSeriesData)-nrow(consistencyData))/nrow(TwoSeriesData)) *100` %

List of inincomplete property:

```{r,echo=FALSE}
kable(dataSet, format = "markdown")

```

#### KB growth 


```{r,echo=FALSE}

entity<-entityWithDays[entityWithDays$class==unclass[8],]

ND<-NormDist(entity)

graph<-plotEntity(entity)

graph

stab<-CheckND(ND)

```
The normalized distance(ND)= `r ND`

KB growth is 1 if ND<1 or KB growth is 0 if ND>=1

KB growth=`r stab`


### Class dbo Work

[http://dbpedia.org/ontology/Work]

Input: Set file location such as -

```{r}
location<- "/ExperimentalData/DBpedia/"
```

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}

# location<- "C:/Users/rifat/Desktop/R_milan/githubRepo/KBQ2/ExperimentalData/DBpedia/dbo-work.csv"
# dTproperty <- read.csv(location,header = TRUE)

loc<-paste(getwd(),location,sep = "")

loc<-paste(loc,"dbo-work.csv",sep = "")
dTproperty <- read.csv(loc,header = TRUE)


dTproperty=plyr::rename(dTproperty, c("count33"="2009-05-20", "count34"="2009-09-20","count201504"="2015-02-05","count201510"="2015-10-02","count35"="2010-03-16","count36"="2010-10-11",
                           "count37"="2011-07-22","count38"="2012-06-01","count39"="2013-0-03","count40"="2014-05-02","count35.1"="2016-04-01"))


entityData=entityDataSet[entityDataSet$class==unclass[9],]

p<-persistencyPlot(entityData)

```

#### Persistency

Persistency Measure Result:  `r entityData[nrow(entityData),3]` value  `r entityData[nrow(entityData),4]` < `r entityData[nrow(entityData)-1,3]` value  `r entityData[nrow(entityData)-1,4]`. So Persistency=  `r persistencyMeasure(entityData)`
Entity Count for 11 Release:

```{r,echo=FALSE}
kable(entityData[,-c(1)], format = "markdown")
shadeAreaP(p,entityData)

```


#### Historical Persitency

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}
histPer<-histPerAll(entityData)

```

Historical Persistency Measure Result: Total no. of class = `r length(unclass)` and No. of persistency=`r nrow(histPer[histPer$Persistency==0,])`. HistPersistencyMeasure= `r HistPersistencyMeasure(histPer)` %

Releases with persistency values:

```{r,echo=FALSE}
kable(histPer[,-c(1)], format = "markdown")
```


#### Consistency


```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}


FilteredProperty<-FilteredPropertyfun(dTproperty,entityDataSet)
TwoSeriesData<-TwoSeriesDataFun(dTproperty,entityDataSet)
dataSet<-dataSetFun(dTproperty,entityDataSet)
consistencyData<-consistencyDataFun(dTproperty,entityDataSet)

```

No. of inconsistent property = `r nrow(FilteredProperty)`


```{r,echo=FALSE}
#kable(SubSetProp, format = "markdown")

kable(FilteredProperty, format = "markdown")

#head(FilteredProperty)

```

List of Consistent Property over last two version:

```{r,echo=FALSE}
kable(TwoSeriesData, format = "markdown")

n=nrow(TwoSeriesData)+nrow(FilteredProperty)


```

#### Completeness

Total no. of property =`r n` No. of Consistent Property = `r nrow(TwoSeriesData)` No. of incomplete property = `r nrow(consistencyData)`

Percentage of completeness= `r ((nrow(TwoSeriesData)-nrow(consistencyData))/nrow(TwoSeriesData)) *100` %

List of inincomplete property:

```{r,echo=FALSE}
kable(dataSet, format = "markdown")

```

#### KB growth 


```{r,echo=FALSE}

entity<-entityWithDays[entityWithDays$class==unclass[9],]

ND<-NormDist(entity)

graph<-plotEntity(entity)

graph

stab<-CheckND(ND)

```
The normalized distance(ND)= `r ND`

KB growth is 1 if ND<1 or KB growth is 0 if ND>=1

KB growth=`r stab`



### Class foaf Person

[http://xmlns.com/foaf/0.1/Person]

Input: Set file location such as -

```{r}
location<- "/ExperimentalData/DBpedia/"
```

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}

# location<- "C:/Users/rifat/Desktop/R_milan/githubRepo/KBQ2/ExperimentalData/DBpedia/foaf-person.csv"
# dTproperty <- read.csv(location,header = TRUE)

loc<-paste(getwd(),location,sep = "")

loc<-paste(loc,"foaf-person.csv",sep = "")
dTproperty <- read.csv(loc,header = TRUE)

dTproperty=plyr::rename(dTproperty, c("count33"="2009-05-20", "count34"="2009-09-20","count201504"="2015-02-05","count201510"="2015-10-02","count35"="2010-03-16","count36"="2010-10-11",
                           "count37"="2011-07-22","count38"="2012-06-01","count39"="2013-0-03","count40"="2014-05-02","count43"="2016-04-01"))


entityData=entityDataSet[entityDataSet$class==unclass[10],]

p<-persistencyPlot(entityData)

```

#### Persistency

Persistency Measure Result:  `r entityData[nrow(entityData),3]` value  `r entityData[nrow(entityData),4]` < `r entityData[nrow(entityData)-1,3]` value  `r entityData[nrow(entityData)-1,4]`. So Persistency=  `r persistencyMeasure(entityData)`
Entity Count for 11 Release:

```{r,echo=FALSE}
kable(entityData[,-c(1)], format = "markdown")
shadeAreaP(p,entityData)

```


#### Historical Persitency

```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}
histPer<-histPerAll(entityData)

```

Historical Persistency Measure Result: Total no. of class = `r length(unclass)` and No. of persistency=`r nrow(histPer[histPer$Persistency==0,])`. HistPersistencyMeasure= `r HistPersistencyMeasure(histPer)` %

Releases with persistency values:

```{r,echo=FALSE}
kable(histPer[,-c(1)], format = "markdown")
```




#### Consistency


```{r,echo=FALSE,comment=NA,results='hide', message=FALSE, warning=FALSE}


unclass=unique(entityWithDays$class)

en=entityDataSet[entityDataSet$class==unclass[10],]

# dTproperty=normalize(dTproperty,en)

dTproperty<-dTproperty[,order(colnames(dTproperty),decreasing=TRUE)]



head(dTproperty)

NondTproperty=dTproperty

CorrectProperty = identifyCorrectProperty(dTproperty,en)

# InCorrectPropery= identifyInCorrectProperty(NondTproperty,en)


avg=(en[11,]$count+en[10,]$count+en[9,]$count)/3

NondTproperty=dTproperty

d=3
t=11

for(i in 1:11){
     
  countEntity=100#avg/20000#en[t,]$count/10000
  
#   print(countEntity)  
#   print(length(dTproperty[,d]))

  Nonprop=NondTproperty[,d]
  
  for(j in 1:length(Nonprop)){
      
       if(Nonprop[j]>countEntity){
         Nonprop[j]=0
       }
       else{
         Nonprop[j]=Nonprop[j]        
       }
  }
  print(Nonprop)  
  NondTproperty[,d]=Nonprop
  d=d+1
  t=t-1
}

require(data.table)
DT=data.table(NondTproperty)

listCol <- colnames(DT)[grep("-", colnames(DT))]

DT[, Sum := Reduce('+', .SD), .SDcols=listCol][]

NonRproperty=data.frame(DT)

IncorrectProperty=NonRproperty[NonRproperty$Sum!=0,]

head(IncorrectProperty)

# return(IncorrectProperty)


# nrow(NonRproperty)-nrow(IncorrectProperty)
# 
# nrow(Rproperty)-nrow(CorrectProperty)

NdTproperty=CorrectProperty[,-c(14)]

propertySubSet=data.frame(property=IncorrectProperty[,1],v201604=IncorrectProperty[,3],v201510=IncorrectProperty[,4],v201502=IncorrectProperty[,5])


require(data.table)
DT=data.table(propertySubSet)

listCol <- colnames(DT)[grep("v", colnames(DT))]

DT[, Sum := Reduce('+', .SD), .SDcols=listCol][]

propertySubSet=data.frame(DT)

FilteredProperty=propertySubSet[propertySubSet$Sum!=0,]

FilteredProperty=FilteredProperty[,-c(5)]

nrow(FilteredProperty)

# normalize(NdTproperty,en)
d=3
t=11
for(i in 1:11){

    norm= NdTproperty[,d]/avg#$en[t,]$count

    NdTproperty[,d]=norm
    d=d+1
#     print(norm)
    t=t-1
}

NdTproperty$diffLast=NdTproperty[,3]-NdTproperty[,4]

# print(dTproperty)
# head(dTproperty)

# NdTproperty$diffLast=dTproperty[,3]-dTproperty[,4]

consistencyData=NdTproperty[NdTproperty$diffLast<0,]

nrow(dTproperty)

nrow(consistencyData)

dataSet=data.frame(property=consistencyData$property,Version201604=consistencyData$X2016.04.01,Version201510=consistencyData$X2015.10.02,NormFreqDiff=consistencyData$diffLast)

entityVal=en

entityVal$WeightValue=100#en$count/10000

CorrectProperty$diff=CorrectProperty[,3]+CorrectProperty[,4]

TwoSeries=CorrectProperty[CorrectProperty$diff!=0,]

TwoSeriesData=data.frame(Property=TwoSeries$property,version201604=TwoSeries$X2016.04.01,version201510=TwoSeries$X2015.10.02,version201504=TwoSeries$X2015.02.05)


InCdata=data.frame(Property=InCorrectPropery$property,v201604=InCorrectPropery$X2016.04.01,v201510=InCorrectPropery$X2015.10.02,v201502=InCorrectPropery$X2015.02.05)


```

No. of inconsistent property = `r nrow(FilteredProperty)`

```{r,echo=FALSE}
#kable(SubSetProp, format = "markdown")
kable(FilteredProperty, format = "markdown")
#head(FilteredProperty)

```

List of Consistent Property over last two version:

```{r,echo=FALSE}
kable(TwoSeriesData, format = "markdown")
n=nrow(TwoSeriesData)+nrow(FilteredProperty)

```

#### Completeness

Total no. of property =`r n` No. of Consistent Property = `r nrow(TwoSeriesData)` No. of incomplete property = `r nrow(consistencyData)`

Percentage of completeness= `r ((nrow(TwoSeriesData)-nrow(consistencyData))/nrow(TwoSeriesData)) *100` %

List of inincomplete property:

```{r,echo=FALSE}
kable(dataSet, format = "markdown")

```

#### KB growth 


```{r,echo=FALSE}

entity<-entityWithDays[entityWithDays$class==unclass[10],]

ND<-NormDist(entity)

graph<-plotEntity(entity)

graph

stab<-CheckND(ND)

```

The normalized distance(ND)= `r ND`

KB growth condition is 1 if ND<1 or KB growth is 0 if ND>=1

KB growth=`r stab`

